\section{Indoor Positioning}
In outdoor environments, we rely on satellite-based positioning systems, such as \gls{gps}. \gls{gps} is a U.S utilization that is used by both civilians and the military. To get accurate positioning, navigation and timing services, different components are used: \cite{GPSofficial}

\begin{itemize}
    \item Space component is operated by satellites that transmit signals to users on geographical locations and timestamps. 
    \item Control component consists of different elements: 
    \begin{itemize}
        \item Monitor Stations tracks the \gls{gps} satellites as they pass and feed observations to the Master Control Station. 
        \item Master Control Station computes precise locations of the satellites.
        \item Ground Antennas communicate with satellites. 
    \end{itemize}
    \item User component consists of \gls{gps} receivers or transmitters, including telematic devices, smartphones and etc. 
\end{itemize}

However, the issue with \gls{gps} is that it looses its accuracy when used indoor due to the device not being in line of sight, meaning the device does not have a clear sight to the sky. This is needed for the satellite to place a more accurate position\cite{GPSofficial}. This is due to the reason that signals cannot penetrate through materials, such as glass, brick, metal, etc.\cite{GPSofficial}. \gls{gps} signals are also classified as part of \gls{uhf}, which results in another problem as in an indoor environment, there are potential sources of \gls{uhf} signals which can interfere with the \gls{gps} signal. For example, TV antenna signals can interfere with \gls{gps} signals\cite{GPSofficial}.
This is the reason why we need other technologies when we want to estimate the indoor location. \gls{ips} is a term which covers different technologies that use mobile devices to exploit their physical location. %After an \gls{ips} is developed, it is possible to make use of location-based services.

%https://blog.mapspeople.com/mapsindoors/indoor-positioning-101%
%https://blog.mapspeople.com/mapsindoors/indoor-positioning-101