\section{Task Definition}
Throughout this chapter, we will be conducting experiments with the purpose of solving the problem statement. To help in the process of conducting the experiments, we need to reify the objectives of the experiments. To this end, we have defined sub-tasks with respect to the problem statement, which we can use as goals for the experiments. The problem, which we are working on, is to identify the position in an indoor environment given data collected by a smart phone. The position is specified as a X-coordinate, Y-coordinate and floor level. To this end, we can define sub-tasks for identifying each of the specifications:
\begin{center}
    \textbf{Estimate the X-coordinate}
\end{center}
\vspace{-0.65cm}
\begin{center}
    \textbf{Estimate the Y-coordinate}
\end{center}
\vspace{-0.65cm}
\begin{center}
    \textbf{Estimate the Floor level}
\end{center}

The reasoning for defining these sub-tasks of the separately contrary to define them together is due to the fact that we expect that for the learning based positioning methods, a more specialised model will probably yield more accurate estimations. If a model needs to estimate a combination of the positional parameters, like X, Y, and Floor together, the model would need to capture more complex patterns. However, it might also be the case that a combination of the positional parameters might yield better results, but as we expect that the specialised models for each parameter will have better performance, we will start with testing this type of model. If we do have more time, we can consider to test predicting different combinations of the positional parameters. The \gls{pdr} is limited to estimating X and Y, which will be the sub-tasks that will be tested on this method. For the learning based methods, we will be training models, which are site specific.

%Even though the sub-tasks are defined as three separate tasks, it might be ideal to combine them when conducting an experiment. For example, it might the case that a relationship between the X- and Y-coordinates exists or between all of the sub-tasks. This might lead to a model which solves more than one sub-tasks being superior to a model which is specialised only towards one of the sub-tasks. 
